\begin{itemize}
\item {\large \textbf{Finance Chair}}
\begin{itemize}
\item IEEE International Symposium on Information Theory (ISIT) \hfill{2024}
\end{itemize}
\item {\large \textbf{Technical Societies Committee Member:}}
\begin{itemize} 
\item \textbf{Elected Member}\\
\textsl{IEEE Signal Processing Theory and Methods} \hfill{2018 -- 2023}\\
\textsl{ IEEE Signal Processing for Communications and Networking} \hfill{2018 -- 2020}
\item \textbf{Invited Member}\\
\textsl{ IEEE Signal Processing Education Committee}  \hfill{2022 -- 2023}\\
\textsl{ IEEE Signal Processing for Communications} \hfill{2016 -- 2022}\\
\textsl{ IEEE Multimedia Communications Technical Committee} \hfill{2012 -- 2014}
\end{itemize}\vspace{.1 in}

\item {\large \textbf{Society Representation}}
\begin{itemize}
\item IEEE Signal Processing Society's Representative on the IEEE Smart Grid Initiative \hfill{2019 -- 2023}
\item IEEE Signal Processing Society's Representative on the IEEE Trans. on Smart Grid \hfill{2019 -- 2023}
\end{itemize}
\item {\large \textbf{Technical Chair}} 
\begin{itemize}
\item IEEE Global Communications Conf. (Globecom)\hfill{2020}
\item  Asilomar Conference on Signals, Systems, and Computers \hfill{2020}
\end{itemize}
\item {\large \textbf{Symposium Chair}} 
\begin{itemize} 
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2023}
\item IEEE Global Communications Conf. (Globecom)\hfill{2019}
\item IEEE Intl. Conf. on Computing, Networking and Communications (ICNC)\hfill{2014}
\item IEEE Intl. Conf. on Communications and Networking \hfill{2012}
\end{itemize}\vspace{.1 in}
\item {\large \textbf{Special Session Organizer}}
\begin{itemize} 
\item Asilomar Conference on Signals, Systems, and Computers \hfill{2018}
\item Asilomar Conference on Signals, Systems, and Computers \hfill{2014}
\item  IEEE Workshop on CAMSAP\hfill{2015}
\end{itemize}\vspace{.1 in}
\item {\large \textbf{Track Chair}} 
\begin{itemize}
\item IEEE Statistical Signal Processing Workshop \hfill{2023}
\end{itemize}

\item {\large \textbf{Tutorials Chair}} 
\begin{itemize}
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2020}
\end{itemize} \itemsep=-0.05 in
\item {\large \textbf{Technical Program Committee}} 
\begin{itemize} 
\item  Artificial Intelligence and Statistics (AISTATS) \hfill{2025}
\item International Conference on Learning Representations (ICLR) \hfill{2025}
\item The Conference on Uncertainty in Artificial Intelligence (UAI) \hfill{2024}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2024}
\item IEEE Workshop on Comp. Advances in Multi-Sensor Adaptive Processing (CAMSAP) \hfill{2023}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2023}
\item IEEE Intl. Workshop on Signal Processing Advances in Wireless Communications (SPAWC) \hfill{2022}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2022}
\item IEEE International Symposium on Information Theory (ISIT) \hfill{2021}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2021}
\item IEEE Intl. Workshop on Signal Processing Advances in Wireless Communications (SPAWC) \hfill{2021}
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2020}
\item IEEE International Symposium on Information Theory (ISIT) \hfill{2020}
\item IEEE Intl. Workshop on Signal Processing Advances in Wireless Communications (SPAWC) \hfill{2020}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2020}
\item ACM Special Interest Group on Measurement and Evaluation (SIGMETRICS) \hfill{2020}
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2019}
\item IEEE Global Signal and Information Processing (GlobalSIP)\hfill{2019}
\item IEEE International Symposium on Information Theory (ISIT) \hfill{2019}
\item IEEE Data Science Workshop (DSW) \hfill{2019}
\item IEEE Wireless Communications and Networking Conf. (WCNC) \hfill{2019}
\item IEEE Intl. Workshop on Signal Processing Advances in Wireless Communications (SPAWC) \hfill{2019}
\item IEEE Intl. Conf. on Communications (ICC) \hfill{2019}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2019}
\item IEEE Global Signal and Information Processing (GlobalSIP)\hfill{2018}
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2018}
\item IEEE Global Communications Conf. (Globecom)\hfill{2018}
\item IEEE Intl. Conf. on Communications (ICC) \hfill{2018}
\item IEEE Intl. Conf. on Computing, Networking and Communications (ICNC)\hfill{2018}
\item IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP) \hfill{2018}
\item IEEE Global Communications Conf. (Globecom)\hfill{2017}
\item IEEE Intl. Conf. on Communications (ICC)\hfill{2017}
\item IEEE Global Signal and Information Processing (GlobalSIP)\hfill{2017}
\item IEEE Workshop on Comp. Advances in Multi-Sensor Adaptive Processing (CAMSAP) \hfill{2017}
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2016}
\item IEEE Global Communications Conf. (Globecom)\hfill{2016}
\item IEEE Global Signal and Information Processing (GlobalSIP)\hfill{2016}
\begin{itemize}
\item Machine Learning for of Cognitive Communications and Radar
\item Signal Processing for Big Data in Wireless Networks 
\end{itemize}
\item IEEE Wireless Communications and Networking Conf. (WCNC) \hfill{2016}
\item IEEE Computational Advances in Multi-Sensor Adaptive Processing (CAMSAP)\hfill{2015} 
\item IEEE Global Signal and Information Processing (GlobalSIP) \hfill{2015}
\item IEEE Global Communications Conf. (Globecom) \hfill{2015}
\item IEEE Intl. Conf. on Communications (ICC)\hfill{2015}
\item IEEE Global Signal and Information Processing (GlobalSIP)\hfill{2014}
\item IEEE Intl.  Symposium on Wireless Personal Multimedia Communication (WMPC) \hfill{2014} 
\item IEEE International Wireless Symposium (IWS) \hfill{2014} 
\item IEEE International Conf. on Communications (ICC)\hfill{2014} 
\item IEEE International Conf. on Connected Vehicles \& Expo \hfill{2013} 
\item IEEE \& CIC International Conf. on Communications \hfill{2013} 
\item IEEE Smart Grid Communication Conf. (SmartGridComm)\hfill{2013} 
\item IEEE Global Wireless Summit, \hfill{2013}
\item IEEE Wireless Conf. and Networking Conference \hfill{2013} 
\item IEEE Global Signal and Information Processing (GlobalSIP)\hfill{2013} 
\begin{itemize}
\item Symposium on Network Theory 
\item Symposium on New Sensing and Statistical Inference Methods 
\item Symposium on Information Processing in Energy Grids 
\end{itemize}
\item IEEE International Wireless Symposium \hfill{2013} 
\item IEEE Smart Grid Communications (SmartGridComm)\hfill{2012} 
\end{itemize}\vspace{.1 in}
\item {\large \textbf{Peer Reviewing (Selected List)}}
\begin{itemize} \itemsep=-0.05 in
\item IEEE Transactions on Information Theory
\item Annals of Statistics
\item Bernoulli Journal
\item IEEE Transactions on Automatic Control
\item IEEE Transactions on Signal Processing
\item IEEE Journal of Selected Topics in Signal Processing
\item IEEE Transactions on Signal and Information Processing over Networks
\item IEEE Transactions on Power Systems
\item IEEE Transactions on Smart Grids
\item IEEE Transactions on Communications
\item IEEE Transactions on Wireless Communications
\item IEEE Journal of Selected Areas in Communications
\item IEEE Transactions on Mobile Computing
\item IEEE Transactions on Vehicular Technology
\item IEEE/ACM Transactions on Networking
\item IEEE Signal Processing Magazine
\item IEEE Communications Magazine
\item IEEE Signal Processing Letters
\item IEEE Communication Letters
\item  IEEE Wireless Communications Letters
\item EURASIP Journal on Advances in Signal Processing
\item EURASIP Journal on Wireless Communications and Networking
\item Cambridge University Press
\item ASME Journal of Mechanical Design
\item Conferences: AISTATS, NeurIPS, COLT, ICML, ISIT, INFOCOM, Globecom, ICC, and ICASSP.
\end{itemize}
\end{itemize}
