
\begin{etaremune}
\item \textbf{Matthew McCall} (Computer Science) \hfill May 2024 -- Present \\
Project: \emph{Implementation of topologically consistent point localization procedures in PCMS.}
\item \textbf{James Park} (Computer Science) \hfill  Sept. 2025 -- Present\\
Project: \emph{Implementation of M3DC1 shape functions into PCMS for MHD coupling.}

\item \textbf{Joyal Mathew} (Computer Science) \hfill May 2025 -- Dec. 2025 \\
Project: \emph{Implementation of a simplified field interface in PCMS.}
\item \textbf{Liam Hutchison} (Mechanical Engineering) \hfill Sept. 2024 -- May 2025 \\
Project: \emph{Estimating parameter uncertainty of viscoelastic models using Dakota.}
\item \textbf{Fallon Sannes} (Biomedical Engineering) \hfill Jan. 2025 -- Apr. 2025 \\
Project: \emph{Updating MuMFiM to remove PCU singleton.}

\item \textbf{Flynn McCallum} (Computer Science) \hfill Jan. 2024 -- Dec. 2024 \\
Project: \emph{Removing singleton from PCU.}
\item \textbf{Paul Khoury} (Mechanical Engineering) \hfill Dec. 2023 -- Nov. 2024 \\
Project: \emph{FEM modeling of human sacrum.}
\item \textbf{Ian Gannon} (Mechanical Engineering) \hfill Jun. 2024 -- Aug. 2024 \\
Project: \emph{Modeling viscoelastic glass in FENICS and MFEM.}
\item \textbf{Kulindu Cooray} (Computer Science) \hfill  Aug. 2023 -- May. 2024\\
Project: \emph{Python support for PCMS.}
\item \textbf{Zachary Knowlan} (Mechanical Engineering) \hfill Nov. 2023 -- May 2024 \\
Project: \emph{Modeling viscoelastic glass in FENICS and MFEM.}
\end{etaremune}