
\begin{etaremune}
\item \textbf{Huzaifa Arif} (ECSE) -- Advisor: Alex Gitten\\
Candidacy \hfill TBD
\item \textbf{Zhengye Yang} (ECSE) -- Advisor: Richard Radke \\
Candidacy \hfill TBD
\item \textbf{Quan Xiao} (ECSE) -- Advisor: Tianyi Chen \\
Candidacy \hfill TBD
\item \textbf{Shukai Chen} (ECSE) -- Advisor: Alhussein Abouzeid\\
Candidacy \hfill TBD
\item \textbf{Hongkang Li} (ECSE) -- Advisor: Meng Wang\\
Final Defense \hfill Nov. 2024
\item \textbf{Naiyu Yin} (ECSE) -- Advisor: Qiang Ji\\
Final Defense \hfill Nov. 2024
\item \textbf{Yating Zhou} (ECSE) -- Advisor: Meng Wang\\
Candidacy \hfill Nov. 2024
\item \textbf{Glory Justin} (ECSE) -- Advisor: Santiago Paternain \\
Final Defense \hfill Jul. 2024
\item \textbf{Jiajin Zhang} (BME) -- Advisor: Pingkun Yan\\
Final  Defense \hfill Jun. 2024
\item \textbf{Garo Bedonian} (MANE) -- Advisor: Jason Hicken \\
Final Defense \hfill Mar. 2024
\item \textbf{Lisha Chen} (ECSE) -- Advisor: Tianyi Chen\\
Candidacy \hfill Jul. 2023
\item \textbf{Anika Saha} (CS) -- Advisor: Alex Gitten \\
Final Defense \hfill Jun. 2023
\item \textbf{Ming Yi} (ECSE) -- Advisor: Meng Wang \\
Final Defense \hfill Nov. 2022
\item \textbf{Hengtao Guo} (BME) -- Advisor: Pingkun Yan\\
Final Defense \hfill Nov. 2022
\item \textbf{Yu Wang} (ECSE) -- Advisor: Alhussein Abouzeid \\
Final Defense \hfill May 2022
\item \textbf{Shuai Zhang} (ECSE) -- Advisor: Meng Wang \\
Final Defense \hfill Nov. 2021
\item \textbf{Bariscan Yonel} (ECSE) -- Advisor: Birsen Yaz{\i}c{\i}\\
Final Defense \hfill Nov. 2020
\item \textbf{Gourav Saha} (ECSE) -- Advisor: Alhussein A. Abouzeid\\
Final Defense \hfill Jun. 2020
\item \textbf{Meng Zhang} (ECSE) -- Advisor: Richard Radke\\
Final Defense \hfill May 2020
\item \textbf{Sun Ke} (Imperial College, London, UK)\\
Viva Voce  \hfill Nov. 2019
\item \textbf{Yuan Liu} (ECSE) -- Advisor: John Woods\\
Final Defense \hfill Sep. 2019 
\item \textbf{Yingshuai Hao} (ECSE) -- Advisor: Meng Wang\\
Final defense \hfill Nov. 2018
\item \textbf{Il-Young Son} (ECSE) -- Advisor: Birsen Yaz{\i}c{\i}\\
Final Defense \hfill Nov. 2018 
\item \textbf{Eric Mason} (ECSE) -- Advisor: Birsen Yaz{\i}c{\i}\\ 
Final defense \hfill Nov. 2017
\item \textbf{Hanchao Liu}, (ECSE) -- Advisor:  Jian Sun\\
Final defense \hfill Jul. 2017
\item \textbf{Zhe Wang} (Columbia University, EE) -- Advisor: Xiaodong Wang\\
Final defense \hfill Dec. 2015
\item \textbf{Ning Zheng} (ECSE) --  Advisor: Tong Zhang\\
Final defense \hfill Nov. 2015
\end{etaremune}
